### 2024-06-01 2024-5-13/sections/implementation.tex
update description for ComplexCounting benchmark suite and explanation for experiment results

\medskip
\noindent
\emph{ComplexCounting benchmark suite.} This benchmark suite is generated by the extension of \textsc{stringfuzz} \cite{stringfuzz}. We extend the \textsc{stringfuzz} tool with counting operators and generate 1,000 instances in which half of them contain complement on the counting operators and the other half contain nested counting. The length bound is set to $|x| > 50$ for each string variable $x$.

\medskip
\noindent
\emph{Distribution of problem instances w.r.t. counting bounds. }
The distribution of problem instances w.r.t. the counting bounds in the three suites is shown in Fig~\ref{fig:count_distri}, where the $x$-axis represents the counting bound and the $y$-axis represents the number of problem instances containing the counting bound. 
%The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$). 
From Fig~\ref{fig:count_distri}, we can see that while most problem instances contain only small bounds, there are still around 3,000  (about 6\%) of them using large counting bounds (i.e. greater than or equal to $50$).
%Although most upper bounds are small, about two thousand of them are still greater than 50.

@@

\subsubsection{Empirical justification of the size-reduction technique for register-representable regexes}
We compare $\ostrichrecl$ with its variant ${\rm -ASR}$.  ${\rm -ASR}$ is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 of Section~\ref{subsec:cefadec}). 
The experiment results can be found in Table~\ref{tab:results_heuristic}. We can see that $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than ${\rm -ASR}$. Therefore,  the automata size-reduction technique indeed plays an essential role in the performance improvement.

@@

The ComplexCounting benchmark experiment results is shown in Table~\ref{tab:results_heuristic_complex}. We can see that $\ostrichrecl$ solves 82/339/326 more instances and is 1.02/1.92/1.61 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively.

From the results, the heuristic for complement on counting operators and the heuristic for finding the accepted word of the automaton are more effective than the heuristic for nested counting. Futhermore, the heuristic for complement on counting operators contributes both to satisfiable and unsatisfiable instances, while the heuristic for finding the accepted word and the heuristic for nested counting contribute only to satisfiable instances.
All the optimizations improve the performance of $\ostrichrecl$.

>>>>

\medskip
\noindent
\emph{ComplexCounting benchmark suite.} This benchmark suite is generated by string fuzzing test tool \textsc{stringfuzz} \cite{stringfuzz} extended with the counting operator. We generate 500 instances of the nesting of counting operators containing the RECL constraint $x\in e_{nest}\wedge x\in e_{sani}\wedge |x|>50$ in each of them, where $e_{nest}\equiv (e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}})^{\{m_4,n_4\}}$ is a regex of the nesting of counting operators and $e_{sani} \equiv \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}$ is as RegCoL benchmark suite. Note that $0\leq m_i\leq n_i\leq 20$ for $i\in [4]$ and $e_i$ containing no counting operators for $i\in [3]$ is randomly generated.  We also generate 500 instances of the nesting of counting operators and a complement operator containing the RECL constraint $x\in e_{nest}\wedge x\in e_{comp} \wedge x\in e_{sani} \wedge |x|>50$ in each of them, where $e_{comp}\equiv \overline{e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}}}$ is a regex of the nesting of counting operators and a complement operator, and $e_{nest}$ and $e_{sani}$ are as above. Note that $20\leq m_i\leq n_i\leq 1000$ and $e_i$  containing no counting operators for $i\in [3]$ is randomly generated.

\medskip
\noindent
\emph{Distribution of problem instances w.r.t. counting bounds. }
The distribution of problem instances w.r.t. the counting bounds in the three suites is shown in Fig~\ref{fig:count_distri}, where the $x$-axis represents the counting bound and the $y$-axis represents the number of problem instances containing the counting bound. 
%The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$). 
In our statistics, while most problem instances contain only small bounds, there are still around 3,000  (about 6\%) of them using large counting bounds (i.e. greater than or equal to $50$).
%Although most upper bounds are small, about two thousand of them are still greater than 50.

@@

\subsubsection{Empirical justification of the optimizations for register-representable regexes}
We compare $\ostrichrecl$ with its variant ${\rm -ASR}$.  ${\rm -ASR}$ is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 of Section~\ref{subsec:cefadec}). 
The experiment results can be found in Table~\ref{tab:results_heuristic}. We can see that $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than ${\rm -ASR}$. Therefore,  the automata size-reduction technique indeed plays an essential role in the performance improvement.

@@

Since the non-register-representable regexes collected from real world are few (5\% of RegCoL and AutomatArk benchmark suites) and simple, there seems no much difference between the performance of $\ostrichrecl$ and its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$ in the overall experiment results. Therefore, we consider the ComplexCounting benchmark suite, which contains more complex non-register-representable regexes, to justify the optimizations for non-register-representable regexes. The ComplexCounting benchmark experiment results is shown in Table~\ref{tab:results_heuristic_complex}. We can see that $\ostrichrecl$ solves 82/339/326 more instances and is 1.02/1.92/1.61 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively. From the results, we can conclude that all the optimizations sharply improve the performance of $\ostrichrecl$ on the complex non-register-representable regexes.
